The Splashback Radius of Planck-SZ clusters

### 2018-11-15 Paper_new/RSP_paper_new.tex

\begin{figure}
    \includegraphics[scale=0.55]{Planck_summary.pdf}
\caption{Visualization of the distribution of the masses and redshifts of the used
clusters from the PSZ2 catalog.}
   \label{fig:placnk_summary}
\end{figure}

@@

We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$ in
order to have a similar redshift range as used in
\citet{more2016detection}. Due to the larger beam size of the Planck
satellite, the cluster positions as reported in the catalog may be
mis-centered from the true centers of the galaxy clusters. We perform
a visual inspection of Pan-STARRS images taken around the detected
galaxy clusters in order to locate the nearest, brightest cluster
galaxy (BCG). We regard the position of the BCG as the true cluster
location, under the assumption that the BCG is located at the true,
gravitational center. Due to this crude assumption, we additionally 
study the effects of a possible, remaining mis-centering of the 
cluster positions in our model for the two-dimensional correlation 
function (see Appendix~\ref{sec:mis-centering}).

@@

\begin{figure*}
    \includegraphics[width= \textwidth]{color_vs_z.pdf}
\caption{Scatter plot showing the $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ colors
of the matched galaxies versus their redshifts, where the red dots correspond
to galaxies identified as red from the SDSS spectroscopic colors and blue dots
correspond to galaxies identified as blue, respectively. The black, solid line
indicates the spline cut separating the two populations and excluding the red 
galaxies from the blue population at a confidence level of $3 \sigma$.}
   \label{fig:g-r_vs_z} 
\end{figure*}

>>>>

\begin{figure}
    \includegraphics[scale=0.55]{Planck_summary.pdf}
\caption{The distribution of the masses and redshifts of the galaxy clusters
from the PSZ2 catalog that we use in our analysis. The histograms on the right
hand side and the bottom show the distribution in mass and redshift,
respectively.}
   \label{fig:planck_summary}
\end{figure}

@@

We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$ in order to
have a similar redshift range used in \citet{more2016detection}. The mass and
the redshift distribution of the Planck clusters we use is shown in
Fig.~\ref{fig:planck_summary}. Due to the larger beam size of the Planck
satellite, the cluster positions as reported in the catalog may be
mis-centered from the true centers of the galaxy clusters. We perform
a visual inspection of Pan-STARRS images taken around the detected
galaxy clusters in order to locate the nearest, brightest cluster
galaxy (BCG). We regard the position of the BCG as the true cluster
location, under the assumption that the BCG is located at the true,
gravitational center. Due to this crude assumption, we additionally 
study the effects of a possible, remaining mis-centering of the 
cluster positions in our model for the two-dimensional correlation 
function (see Appendix~\ref{sec:mis-centering}).

@@

    \includegraphics[width= \textwidth]{color_vs_z.pdf}
\caption{Scatter plot showing the $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ colors
of the matched galaxies versus their redshifts, where the red dots correspond
to galaxies identified as red from the SDSS spectroscopic colors and blue dots
correspond to galaxies identified as blue, respectively. The black, solid line
indicates the spline cut separating the two populations and excluding the red 
galaxies from the blue population at a confidence level of $3 \sigma$.}
   \label{fig:g-r_vs_z} 
\end{figure*}
